Staged Abstract Interpreters

### 2019-09-11 paper/10_intro.tex
misc

Roughly at the same time abstract interpretation was proposed,
\citet{futamura1971partial} observed a close connection between interpreters and
compilers through a hierarchy of specializations, known since then as the
Futamura projections. The first Futamura projection states that specializing an
interpreter to an input program removes interpretative overhead and yields an
equivalent executable that runs faster. In recent years, the idea of Futamura
projections has attracted more attention, and has been successfully applied to
many real-world problems, including query compilers
\cite{DBLP:conf/sigmod/TahboubER18}, PyPy \cite{Bolz:2009:TMP:1565824.1565827},
Truffle \cite{Marr:2015:TVP:2814270.2814275}, etc. The challenge here: can we
apply Futamura projections to a general abstract interpreter to make it run
faster? The solution is not obvious, as we need to specialize a nonstandard
semantics that extensively uses nondeterminism, operates on abstract domains,
and computes fixed-points iteratively over caches.

>>>>

Roughly at the same time abstract interpretation was proposed,
\citet{futamura1971partial} observed a close connection between interpreters and
compilers through a hierarchy of specializations, known since then as the
Futamura projections. The first Futamura projection states that specializing an
interpreter to an input program removes interpretative overhead and yields an
equivalent executable that runs faster. In recent years, the idea of Futamura
projections has attracted more attention, and has been successfully applied to
many real-world problems, including PyPy \cite{Bolz:2009:TMP:1565824.1565827},
Truffle \cite{Marr:2015:TVP:2814270.2814275}, query compilers
\cite{DBLP:conf/sigmod/TahboubER18}, etc. The challenge here: can we apply
Futamura projections to a general abstract interpreter to make it run faster?
The solution is not obvious, as we need to specialize a nonstandard semantics
that extensively uses nondeterminism, operates on abstract domains, and
computes fixed-points iteratively over caches.
